My catchy title for a manuscript

### 2017-12-12 code.Rmd
updates on paths

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(readxl)
library(viridis)
library(ggthemes)
library(lme4)
library(cowplot)
library(broom)
library(agricolae)
library(lattice)
library(influence.ME)
```

@@

```{r message=FALSE, warning=FALSE}
perithecia <- read_csv("./data/perithecia.csv") %>%
  filter(genotype != "t")

@@

### Transform
The data were prepared in the wide format where each score for percent perithecia coverage (0 -3) is in a separate colum. Let's transform this dataframe from the wide to the long format using `gather` function of `dplyr`. We need to create a column for the variable name and another for the score.

@@

```{r message=FALSE, warning=FALSE}
grid1 <- plot_grid(g1, g2, labels = c("A", "B"), align = "hv", ncol = 1)
ggsave("figs/grid1.png", grid1, width = 6, height = 6)
```

@@

```{r message=FALSE, warning=FALSE}
Sys.setlocale("LC_ALL", "pt_BR.UTF-8")
mgr <- read_excel("./data/mycelia.xlsx")

@@

```{r message=FALSE, warning=FALSE}
spor <- read_csv("./data/spor.csv")

@@

### Figure

@@

grid5 <- plot_grid(mgr1, grid1, labels = c("A"), rel_heights = c(1, 1), ncol = 1, align = "hv")
ggsave("figs/mgr_spor_germ.png", grid5, width = 5, height = 5)

@@

```{r message=FALSE, warning=FALSE}
pathogen <- read_csv("./data/pathogenicity.csv")
pathogen <- pathogen %>%
  filter(isolate != "test")
```

@@

>>>>

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(here)
library(readxl)
library(viridis)
library(ggthemes)
library(lme4)
library(cowplot)
library(broom)
library(agricolae)
library(lattice)
library(influence.ME)
```

@@

```{r message=FALSE, warning=FALSE}
perithecia <- read_excel(here("data", "all-data.xlsx"), "perithecia") %>%
  filter(genotype != "t")

@@

The data were prepared in the wide format where each score for percent perithecia coverage (0 -3) is in a separate colum. Let's transform this dataframe from the wide to the long format using `gather` function of `dplyr`. We need to create a column for the variable name and another for the score.

@@

```{r message=FALSE, warning=FALSE}
grid1 <- plot_grid(g1, g2, labels = c("A", "B"), align = "hv", ncol = 1)
ggsave(here("figs", "figure1.png"), grid1, width = 6, height = 6)
grid1
```

@@

```{r message=FALSE, warning=FALSE}
Sys.setlocale("LC_ALL", "pt_BR.UTF-8")
mgr <- read_excel(here("data", "all-data.xlsx"), "mycelia")

@@

```{r message=FALSE, warning=FALSE}
spor <- read_excel(here("data", "all-data.xlsx"), "spor_germ")

@@

### Figure 3

@@

grid5 <- plot_grid(mgr1, grid1, labels = c("A"), rel_heights = c(1, 1), ncol = 1, align = "hv")
ggsave(here("figs", "figure3.png"), grid5, width = 5, height = 5)

@@

```{r message=FALSE, warning=FALSE}
pathogen <- read_excel(here("data", "all-data.xlsx"), "pathogenicity") %>%
  filter(isolate != "test")
```

@@

## Fungicide sensitivity

```{r message=FALSE, warning=FALSE}
ec50 <- read_excel(here("data", "all-data.xlsx"), "ec50") 
```

### Summarize

```{r}
ec502 <- ec50 %>%
  group_by(isolate, species, genotype)%>%
  summarize(mean_ec50 = mean(ec50),
            sd_ec50 = sd(ec50)
            )
```

Let's have a look at the mean EC50 for the isolates

library(viridis)
library(ggthemes)
ec502 %>%
  ggplot(aes(genotype, mean_ec50, color = species))+
  geom_jitter(width = 0.1)+
  #geom_errorbar(aes(min = mean_ec50 - sd_ec50, max = mean_ec50 + sd_ec50), width=0.2, position = position_dodge(width = 0.2))+
  theme_few()+
  theme(legend.position="right", legend.text=element_text(size=7, face = 'italic'))+
    ylim(0,1.8)+
 scale_color_viridis( discrete = TRUE)+
  labs(y = (expression(paste('EC'[50], ' (', mu,'g/ml)'))), x = "Trichothecene genotype", color="Species")+
  ggsave(here("figs", "ec50-new.png"), width=4.5, height=3)

```

### 2017-12-12 data.Rmd
updates on paths

The data were obtained from xx and were organized in xx excel/csv files. The example file is in the wide format where each day of assessment is in a different column, etc.

## Data wrangling

The original files were modified as following. The names of the variables were changed to.. The original wide format was retained and will be transformed using the dplyr functions, etc.

## Glimpse

```{r message=FALSE, warning=FALSE}
library(tidyverse)
#data <- read_delim("data/data.csv", delim = ";")
glimpse(data)
```

## Description of variables

- Variable1: 
  - Description 
  - Type: character
  - Unit

- Variable2: 
  - Description 
  - Type: integer
  - Unit

- Variable3: 
  - Description 
  - Type: double
  - Unit:

## Quick view

```{r}
data
```

@@

The data are deposited in xx public repositories where they can be downloaded. Check on each data repository the policies regarding data use and citation.

<img src = "https://osf.io/static/img/circle_logo.png" width = "25">
[](DOI 10.17605/OSF.IO/7D3CH)

>>>>

The data were obtained from five different, mostly repeated experiments, and were organized in a single `xlsx` file. Data from each experiment are in a separate sheet, which are loaded separately using the `read_excel` function of the `readxl` file.

`I found much more convenient to use this binary file instead of storing in a text file like csv. For some variabeles, I had to deal with some characters which were not loading correctly when using `csv` files.`

Most of the data are already organized in the long format, but some are in the wide, and so will need some transformation. These are done within the respective section of the data analysis page.

@@

The data are stored in the `data` folder of the GitHub repository.

https://github.com/phytopathology/paper-FGSC-fitness
